European or American? A re-examination of the transatlantic influence over the IMF

### 2025-07-21 manuscript/manuscript.qmd
Add "Western" bloc

>>>>

In the case of the IMF, there is broad consensus that the institution is dominated by “Western” powers. This is reflected in both historical accounts of its founding and institutional design—especially its weighted voting system, which concentrates power in the hands of the United States and European countries [@kahler2001; @barnett2004; @copelovitch2010]. Given the ideological, geopolitical, and economic proximity between the US and major European states, many studies treat “the West” as a unified bloc and do not disaggregate their respective influences [e.g. @lipscy2018; @vreeland2007; @copelovitch2010a].
